---
title: "Download"
author: "Yeshu Aggarwal"
date: "14/02/2022"
output: html_document
---

### GitHub Username: yeshuaggarwal
### Student Name: Yeshu Aggarwal
### Student ID: 20103933

## Project Info

**GitHub Link:** https://github.com/yeshuaggarwal/Rentrez.git

## PART I

### 1. Load Packages

```{r}
install.packages("rentrez")
```

```{r}
ncbi_ids <- c("HQ433692.1","HQ433694.1","HQ433691.1")
```

###Above line of code is used to create vectors for 3 different sequences of the 16S gene of Borrelia burgdorferi (aka Borreliella burgdorferi).

```{r}
library(rentrez)
```

###Above line of code using the function library is used to load the 'rentrez' package into the R.

```{r}
Bburg<-entrez_fetch(db = "nuccore", id = ncbi_ids, rettype = "fasta")
```

###Above line of code is used to get sequences for the organism as a character vector.

```{r}
Bburg
```

```{r}
Sequences<-strsplit(Bburg, split = "\n\n")
print(Sequences)
```

```{r}
Sequences<-unlist(Sequences)
```

```{r}
header<-gsub("(^>.*sequence)\\n[ATCG].*","\\1",Sequences)
header
```

```{r}
seq<-gsub("^>.*sequence\\n([ATCG].*)","\\1",Sequences)
seq
```


```{r}
Sequences<-data.frame(Name=header,Sequence=seq)
Sequences
```

### Remove the newline characters from the Sequences data frame using regular expressions

```{r}
Sequences$Sequence<-gsub("\n", "", as.character(Sequences$Sequence))
```


```{r}
Sequences
```

```{r}
Sequences$Sequence
```
### Output this data frame to a file called Sequences.csv

```{r}
write.csv(Sequences, "C:/Users/yeshu/Desktop/A5_Aggarwal_Yeshu_Sequences.csv", row.names = FALSE)
```











