---
title: "COVIDgenome"
author: "Yeshu Aggarwal"
date: "16/02/2022"
output: html_document
---

### GitHub Username: yeshuaggarwal
### Student Name: Yeshu Aggarwal
### Student ID: 20103933

## Project Info

**GitHub Link:** https://github.com/yeshuaggarwal/Rentrez.git

## PART II

### Download the SARS-CoV-2 reference genome from Genbank.

```{r}
library(Biostrings)
```

```{r}
Seq<- readDNAStringSet("C:/Users/yeshu/Desktop/GCF_009858895.2_ASM985889v3_genomic.fna.gz")
```

```{r}
Seq
```
```{r}
str(Seq)
```

### Use regular expressions in R to isolate the S protein from the genome you downloaded

```{r}
Seq@metadata
```
```{r}
Seq<-unlist(str_split(Seq, "ATGTTTGTTTTTCTTGTTTA-GTCAAATTACATTACACATAA"))
```

```{r}
Seq
```

```{r}
Protein<-substr(Seq, 21563, 25384)
Protein
```

### Would you say this gene is highly conserved or evolving rapidly? Why?

I would say it is evolving rapidly because it has alignments with various other SARS-CoV-2 genomes. There were total of 100 hits for this one protein.

















